---
title: "Capstone_20240128 (EXPLORING the PTC data for 1st time)"
output: html_document
date: "2024-01-28"
---

# OBJECTIVE: 
1. Preparing data about attendance
2. Trying to get the Non-particpant data from the existed data
3. Making a plot of number of each category
4. Counting how many current member from the existed data
5. Ploting the counts of members in each member type
6. Preparing the questions to ask during next week meeting

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
library(dplyr)
library(ggplot2)
```

# Some brainstorm
# How is the variable of event participation linked to member renewal? #
#### For Attendee data ####
```{r}
# please change "XXX" to your laptop name
# Load the Excel file: Event Attendees 2018 through 2023.xlsx
att_data <- "/Users/XXX/Event Attendees 2018 through 2023.xlsx"
sheet <- excel_sheets(att_data)
att_2018data <- read_excel(att_data, sheet = sheet[1])
att_2019data <- read_excel(att_data, sheet = sheet[2])
att_2020data <- read_excel(att_data, sheet = sheet[3])
att_2021data <- read_excel(att_data, sheet = sheet[4])
att_2022data <- read_excel(att_data, sheet = sheet[5])
att_2023data <- read_excel(att_data, sheet = sheet[6])
```

```{r}
cleaned_18att <- att_2018data %>%
  select(-`First Name`, -`Last Name`,  -`Title`, -`Registrant Email`)
cleaned_19att <- att_2019data %>%
  select(-`First Name`, -`Last Name`,  -`Title`, -`Registrant Email`)
cleaned_20att <- att_2020data %>%
  select(-`First Name`, -`Last Name`,  -`Title`, -`Registrant Email`)
cleaned_21att <- att_2021data %>%
  select(-`First Name`, -`Last Name`,  -`Title`, -`Registrant Email`)
cleaned_22att <- att_2022data %>%
  select(-`First Name`, -`Last Name`,  -`Title`, -`Registrant Email`)
cleaned_23att <- att_2023data %>%
  select(-`First Name`, -`Last Name`,  -`Title`, -`Registrant Email`)
```

```{r}
#length(unique(cleaned_18att$`Event Code`))
#length(unique(cleaned_19att$`Event Code`))
#length(unique(cleaned_20att$`Event Code`))
#length(unique(cleaned_21att$`Event Code`))
#length(unique(cleaned_22att$`Event Code`))
#length(unique(cleaned_23att$`Event Code`))
# 75
# 61
# 57
# 39
# 43
# 11
```

#### For 2023 Attendee data ####
```{r}
#create a new col name 'Attendee' and set all values be 1
cleaned_23att$Attendee <- 1
```

```{r}
new_cleaned_23att <- cleaned_23att %>%
  select(-`Register Type`)
new_cleaned_23att <- new_cleaned_23att %>%
  filter(`Company Member Type` %in% c("M", "MN"))
# non-particpant is for the member and new member.
```

```{r}
unique_combinations <- unique(cleaned_23att[, c("Company", "Event Code")])
print(unique_combinations)
```

```{r}
new_cleaned_23att <- new_cleaned_23att %>%
  group_by('Company','Event Code')%>%
  summarise(`Company Member Type` = first(`Company Member Type`),
            `Paid Through Date` = first(`Paid Through`),
            `Join Date` = first(`Join Date`), .groups = 'drop') %>%
  ungroup()
```

```{r}
unique_register_types <- unique(cleaned_23att$'Register Type')
print(unique_register_types)
```

#### For Non-Participant data ####
```{r}
# Load the Excel file: NonParticipant.Members.LastYear.xlsx
Nonpartipant_data <-read_excel("/Users/XXX/NonParticipant.Members.LastYear.xlsx") 
```

```{r}
# remove erased data
Nonpartipant_data <- Nonpartipant_data %>% filter(Company != '(Erased)')
```

```{r}
# already only for member an member new.
Nonpartipant_data <- Nonpartipant_data %>% filter(`Member Type` %in% c("M", "MN"))
# 347 observations
```

```{r}
unique_category_types <- unique(Nonpartipant_data$'Category')
print(unique_category_types)
# "Tech" "Ent"  "NP"   "TU"   "Edu"  NA
```

```{r}
category_counts <- table(Nonpartipant_data$'Category')
```

```{r}
category_data <- data.frame(Category = names(category_counts),
                            Count = category_counts)
```

```{r}
# rename, for the plot
category_data <- category_data %>%
  mutate(Category = ifelse(Category == "Edu", "Education",
                           ifelse(Category == "NP", "Non-Profit", 
                                  ifelse(Category == "Ent", "Entrepreneur",
                                         ifelse(Category == "Tech","Technology",
                                                ifelse(Category == "TU","Technology User", Category))))))
```

```{r}
nonpart_plot <- ggplot(category_data, aes(x = Category, y = Count.Freq)) +
  geom_bar(stat = "identity", fill = "lightgreen") +
  geom_text(aes(label = Count.Freq), vjust = -0.5, size = 4, fontface = "bold") +
  labs(title = "Count of Nonparticipants in Each Category",
       x = "Category",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.6, size = 9),
        axis.title = element_text(size = 12, face = "bold"))+
  ylim(0, max(category_counts) * 1.2)
nonpart_plot
```


#### For Current Member data ####
```{r}
# Load the Excel file: Current.Members.JoinDate.xlsx
CurrentMember_data <-read_excel("/Users/XXX/Current.Members.JoinDate.xlsx") 
```

```{r}
# Check how many current member:
num_cu_member <- nrow(CurrentMember_data)
num_cu_member
# 835
```

```{r}
# Check how many member type
unique_member_types <- unique(CurrentMember_data$'Member Type')
print(unique_member_types)
# "Non-Profit"      "Technology"      "Entrepreneur"    "Education"       "Technology User"
```

```{r}
# Check how many company are in each member type?
member_type_counts <- table(CurrentMember_data$'Member Type')
#print(member_type_counts)
# Education 46    Entrepreneur 156    Non-Profit 60     Technology 396  Technology User 177
```

```{r}
member_count_data <- data.frame(Category = names(member_type_counts),
                                Count = as.numeric(member_type_counts))
```

# Plot the counts of members in each member type
```{r}
member_count_plot <- ggplot(member_count_data, aes(x = Category, y = Count)) +
  geom_bar(stat = "identity", fill = "lightgreen") +
  geom_text(aes(label = Count), vjust = -0.5, size = 4, fontface = "bold") +
  labs(title = "Count of Members in Each Category",
       x = "Category",
       y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 0.6, size = 9),
        axis.title = element_text(size = 12, face = "bold")) +
  ylim(0, max(member_count_data$Count) * 1.2) 
member_count_plot
```

#### Merge data ####
```{r}
#merged_data <- merge(CurrentMember_data, cleaned_23att, by = "Company", all.x = TRUE)
# Current member 835
# ........
```

```{r}
#merged_data$Attendee <- ifelse(is.na(merged_data$Attendee), 0, merged_data$Attendee)
```


#### How is the variable of event participation linked to member renewal? 
1. event participation (attendee/brite) 
2. member renewal (monthly member list )
3. non-participant
4. benefit use
5. job posted
6. scorecard usage

Questions (be ready to ask at meeting with PTC):
## ideally, event participation, which a binary variable indicating whether a member attended an event (1 for attended, 0 for did not attend), and member renewal, also a binary variable indicating whether a member renewed their membership (1 for renewed, 0 for not renewed).

#### What type of engagement levers are helpful in securing renewal? 
- type of engagement levers:
- attending events(attendees) 
- usage of career services? (Job's Posted on Career Connector by Company (only member can post or not?))

#### Regarding the 'Job's Posted on Career Connector by Company
Questions:
- there are some blank in this dataset, meaning?
- Start from 2021 to current, if only member can post on Career Connector, -> any relation b/w renewing membership?









